---
title: "Data 607 Part 1"
author: "Tyler Baker"
date: "12/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
library(jsonlite)
library(data.table)
```


# Create a Table of Player's and their Colleges

In order to complete my project I need to be able to compare nfl player stats and be able to compare each college.

However, finding a table of this is a difficult task. Thus, I have decided to build my own. 

To build a table of each current NFL player and their respective college I will scrape data from "Ourlads" for each NFL team. Then, I will combine all of these into one massive dataframe.

#AFC

## AFC East

### Buffalo Bills

```{r}
bill_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/BUF"
bills_page_scrape <- read_html(bill_url_scrape)
bills_players_table <- html_nodes(bills_page_scrape, 'table')
bills_players <- html_table(bills_players_table)[[1]]
bills_players <- bills_players %>%
  add_column(current_team = "Bills")
```

### Miami Dolphins

```{r}
dolphins_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/MIA"
dolphins_page_scrape <- read_html(dolphins_url_scrape)
dolphins_players_table <- html_nodes(dolphins_page_scrape, 'table')
dolphins_players <- html_table(dolphins_players_table)[[1]]
dolphins_players <- dolphins_players %>%
  add_column(current_team = "Dolphins")
```

### New England Patriots

```{r}
patriots_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/NE"
patriots_page_scrape <- read_html(patriots_url_scrape)
patriots_players_table <- html_nodes(patriots_page_scrape, 'table')
patriots_players <- html_table(patriots_players_table)[[1]]
patriots_players <- patriots_players %>%
  add_column(current_team = "Patriots")
```

### New York Jets

```{r}
jets_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/NYJ"
jets_page_scrape <- read_html(jets_url_scrape)
jets_players_table <- html_nodes(jets_page_scrape, 'table')
jets_players <- html_table(jets_players_table)[[1]]
jets_players <- jets_players %>%
  add_column(current_team = "Jets")
```

## AFC North

### Baltimore Ravens

```{r}
ravens_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/BAL"
ravens_page_scrape <- read_html(ravens_url_scrape)
ravens_players_table <- html_nodes(ravens_page_scrape, 'table')
ravens_players <- html_table(ravens_players_table)[[1]]
ravens_players <- ravens_players %>%
  add_column(current_team = "Ravens")
```

### Cincinnati Bengals

```{r}
bengals_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/CIN"
bengals_page_scrape <- read_html(bengals_url_scrape)
bengals_players_table <- html_nodes(bengals_page_scrape, 'table')
bengals_players <- html_table(bengals_players_table)[[1]]
bengals_players <- bengals_players %>%
  add_column(current_team = "Bengals")
```

### Cleveland Browns

```{r}
browns_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/CLE"
browns_page_scrape <- read_html(browns_url_scrape)
browns_players_table <- html_nodes(browns_page_scrape, 'table')
browns_players <- html_table(browns_players_table)[[1]]
browns_players <- browns_players %>%
  add_column(current_team = "Browns")
```

### Pittsburgh Steelers

```{r}
steelers_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/PIT"
steelers_page_scrape <- read_html(steelers_url_scrape)
steelers_players_table <- html_nodes(steelers_page_scrape, 'table')
steelers_players <- html_table(steelers_players_table)[[1]]
steelers_players <- steelers_players %>%
  add_column(current_team = "Steelers")
```

## AFC South

### Houston Texans

```{r}
texans_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/HOU"
texans_page_scrape <- read_html(texans_url_scrape)
texans_players_table <- html_nodes(texans_page_scrape, 'table')
texans_players <- html_table(texans_players_table)[[1]]
texans_players <- texans_players %>%
  add_column(current_team = "Texans")
```

### Indianapolis Colts

```{r}
colts_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/IND"
colts_page_scrape <- read_html(colts_url_scrape)
colts_players_table <- html_nodes(colts_page_scrape, 'table')
colts_players <- html_table(colts_players_table)[[1]]
colts_players <- colts_players %>%
  add_column(current_team = "Colts")
```

### Jacksonville Jaguars

```{r}
jaguars_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/JAX"
jaguars_page_scrape <- read_html(jaguars_url_scrape)
jaguars_players_table <- html_nodes(jaguars_page_scrape, 'table')
jaguars_players <- html_table(jaguars_players_table)[[1]]
jaguars_players <- jaguars_players %>%
  add_column(current_team = "Jaguars")
```

### Tennessee Titans

```{r}
titans_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/TEN"
titans_page_scrape <- read_html(titans_url_scrape)
titans_players_table <- html_nodes(titans_page_scrape, 'table')
titans_players <- html_table(titans_players_table)[[1]]
titans_players <- titans_players %>%
  add_column(current_team = "Titans")
```

## AFC West

### Denver Broncos

```{r}
broncos_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/DEN"
broncos_page_scrape <- read_html(broncos_url_scrape)
broncos_players_table <- html_nodes(broncos_page_scrape, 'table')
broncos_players <- html_table(broncos_players_table)[[1]]
broncos_players <- broncos_players %>%
  add_column(current_team = "Broncos")
```

### Kansas City Chiefs

```{r}
chiefs_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/KC"
chiefs_page_scrape <- read_html(chiefs_url_scrape)
chiefs_players_table <- html_nodes(chiefs_page_scrape, 'table')
chiefs_players <- html_table(chiefs_players_table)[[1]]
chiefs_players <- chiefs_players %>%
  add_column(current_team = "Chiefs")
```

### Las Vegas Raiders

```{r}
raiders_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/LV"
raiders_page_scrape <- read_html(raiders_url_scrape)
raiders_players_table <- html_nodes(raiders_page_scrape, 'table')
raiders_players <- html_table(raiders_players_table)[[1]]
raiders_players <- raiders_players %>%
  add_column(current_team = "Raiders")
```

### Los Angeles Chargers

```{r}
chargers_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/LAC"
chargers_page_scrape <- read_html(chargers_url_scrape)
chargers_players_table <- html_nodes(chargers_page_scrape, 'table')
chargers_players <- html_table(chargers_players_table)[[1]]
chargers_players <- chargers_players %>%
  add_column(current_team = "Chargers")
```


## AFC Roster

```{r}
afc_east_players <- rbind(bills_players, jets_players, patriots_players, dolphins_players)

afc_north_players <- rbind(browns_players, steelers_players, ravens_players, bengals_players)

afc_south_players <- rbind(texans_players, titans_players, colts_players, jaguars_players)

afc_west_players <- rbind(chiefs_players, raiders_players, broncos_players, chargers_players)

afc_players <- rbind(afc_east_players, afc_north_players, afc_south_players, afc_west_players)
```

# NFC

## NFC East

### New York Giants

```{r}
giants_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/NYG"
giants_page_scrape <- read_html(giants_url_scrape)
giants_players_table <- html_nodes(giants_page_scrape, 'table')
giants_players <- html_table(giants_players_table)[[1]]
giants_players <- giants_players %>%
  add_column(current_team = "Giants")
```

### Dallas Cowboys

```{r}
cowboys_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/DAL"
cowboys_page_scrape <- read_html(cowboys_url_scrape)
cowboys_players_table <- html_nodes(cowboys_page_scrape, 'table')
cowboys_players <- html_table(cowboys_players_table)[[1]]
cowboys_players <- cowboys_players %>%
  add_column(current_team = "Cowboys")
```

### Philadelphia Eagles

```{r}
eagles_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/PHI"
eagles_page_scrape <- read_html(eagles_url_scrape)
eagles_players_table <- html_nodes(eagles_page_scrape, 'table')
eagles_players <- html_table(eagles_players_table)[[1]]
eagles_players <- eagles_players %>%
  add_column(current_team = "Eagles")
```

### Washington Football Team

```{r}
wft_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/WAS"
wft_page_scrape <- read_html(wft_url_scrape)
wft_players_table <- html_nodes(wft_page_scrape, 'table')
wft_players <- html_table(wft_players_table)[[1]]
wft_players <- wft_players %>%
  add_column(current_team = "WFT")
```

## NFC North

### Green Bay Packers

```{r}
packers_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/GB"
packers_page_scrape <- read_html(packers_url_scrape)
packers_players_table <- html_nodes(packers_page_scrape, 'table')
packers_players <- html_table(packers_players_table)[[1]]
packers_players <- packers_players %>%
  add_column(current_team = "Packerss")
```

### Minnesota Vikings

```{r}
vikings_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/MIN"
vikings_page_scrape <- read_html(vikings_url_scrape)
vikings_players_table <- html_nodes(vikings_page_scrape, 'table')
vikings_players <- html_table(vikings_players_table)[[1]]
vikings_players <- vikings_players %>%
  add_column(current_team = "Vikings")
```

### Detroit Lions

```{r}
lions_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/DET"
lions_page_scrape <- read_html(lions_url_scrape)
lions_players_table <- html_nodes(lions_page_scrape, 'table')
lions_players <- html_table(lions_players_table)[[1]]
lions_players <- lions_players %>%
  add_column(current_team = "Lions")
```

### Chicago Bears

```{r}
bears_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/CHI"
bears_page_scrape <- read_html(bears_url_scrape)
bears_players_table <- html_nodes(bears_page_scrape, 'table')
bears_players <- html_table(bears_players_table)[[1]]
bears_players <- bears_players %>%
  add_column(current_team = "Bears")
```

## NFC South

### Carolina Panthers

```{r}
panthers_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/CAR"
panthers_page_scrape <- read_html(panthers_url_scrape)
panthers_players_table <- html_nodes(panthers_page_scrape, 'table')
panthers_players <- html_table(panthers_players_table)[[1]]
panthers_players <- panthers_players %>%
  add_column(current_team = "Panthers")
```

### Atlanta Falcons

```{r}
falcons_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/ATL"
falcons_page_scrape <- read_html(falcons_url_scrape)
falcons_players_table <- html_nodes(falcons_page_scrape, 'table')
falcons_players <- html_table(falcons_players_table)[[1]]
falcons_players <- falcons_players %>%
  add_column(current_team = "Falcons")
```

### Tampa Bay Bucs

```{r}
bucs_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/TB"
bucs_page_scrape <- read_html(bucs_url_scrape)
bucs_players_table <- html_nodes(bucs_page_scrape, 'table')
bucs_players <- html_table(bucs_players_table)[[1]]
bucs_players <- bucs_players %>%
  add_column(current_team = "Bucs")
```

### New Orleans Saints

```{r}
saints_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/NO"
saints_page_scrape <- read_html(saints_url_scrape)
saints_players_table <- html_nodes(saints_page_scrape, 'table')
saints_players <- html_table(saints_players_table)[[1]]
saints_players <- saints_players %>%
  add_column(current_team = "Saints")
```

## NFC West

### Seattle Seahawks

```{r}
seahawks_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/SEA"
seahawks_page_scrape <- read_html(seahawks_url_scrape)
seahawks_players_table <- html_nodes(seahawks_page_scrape, 'table')
seahawks_players <- html_table(seahawks_players_table)[[1]]
seahawks_players <- seahawks_players %>%
  add_column(current_team = "Seahawks")
```

### Los Angeles Rams

```{r}
rams_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/LAR"
rams_page_scrape <- read_html(rams_url_scrape)
rams_players_table <- html_nodes(rams_page_scrape, 'table')
rams_players <- html_table(rams_players_table)[[1]]
rams_players <- rams_players %>%
  add_column(current_team = "Rams")
```

### San Fransisco 49'ers

```{r}
forty_niners_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/SF"
forty_niners_page_scrape <- read_html(forty_niners_url_scrape)
forty_niners_players_table <- html_nodes(forty_niners_page_scrape, 'table')
forty_niners_players <- html_table(forty_niners_players_table)[[1]]
forty_niners_players <- forty_niners_players %>%
  add_column(current_team = "49ers")
```

### Arizona Cardinals

```{r}
cardinals_url_scrape <- "https://www.ourlads.com/nfldepthcharts/roster/ARZ"
cardinals_page_scrape <- read_html(cardinals_url_scrape)
cardinals_players_table <- html_nodes(cardinals_page_scrape, 'table')
cardinals_players <- html_table(cardinals_players_table)[[1]]
cardinals_players <- cardinals_players %>%
  add_column(current_team = "Cardinals")
```

## NFC Roster

```{r}
nfc_east_players <- rbind(cowboys_players, wft_players, eagles_players, giants_players)

nfc_north_players <- rbind(packers_players, vikings_players, lions_players, bears_players)

nfc_south_players <- rbind(panthers_players, saints_players, falcons_players, bucs_players)

nfc_west_players <- rbind(forty_niners_players, seahawks_players, cardinals_players, rams_players)

nfc_players <- rbind(nfc_south_players, nfc_north_players, nfc_east_players, nfc_west_players)
```

## NFL Roster

```{r}
nfl_players <- rbind(afc_players, nfc_players)
```

# Convert to CSV

```{r}
write_csv(nfl_players, "C:\\Users\\tyler\\Downloads\\DATA 607.csv")
```